### 2018-11-24 pilot_manuscript.Rmd
I thnk I got this updated correctly

---
title             : "Moral Foundations of U.S. Political News Organizations"
shorttitle        : "MORAL FOUNDATIONS OF U.S. NEWS"

@@

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)

@@

```{r data-cleanup, eval=TRUE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

#write.csv(final, "finaldata.csv")

####start here####
final = read.csv("finaldata.csv", stringsAsFactors = F)
final = na.omit(final) #one weird NA line

@@

```{r fix-MFD, eval=TRUE, include=FALSE}
##figure out the percent of MFD words

##the amount of time people used the original MFD words
original_mfd = read.csv("original_mfd.csv", stringsAsFactors = F)

##adding forms/conjugations of words to original_mfd
#harm/care
original_mfd[c(27:95),1] = c("abusive","abuser","abused","abusing",
                             "sympathetic","sympathies","damaged",
                             "damaging","attacked","attacking","attacker",
                             "attacks","attackers", "benefits", "benefitted",
                             "benefitting", "cares", "cared", "caring", "crushes",
                             "crushing", "crushed", "dangerous", "defends", "defending",
                             "defended", "detroys", "destroyed", "destroying",
                             "fights", "fought", "fighting", "guards", "guarded",
                             "guarding", "harms", "harmed", "harming", "hurts",
                             "hurting", "kills", "killed", "killing", "preserves",
                             "preserved", "preserving", "protects", "protected",
                             "protecting", "protection", "ruins", "ruined", "ruining",
                             "safely", "safer", "shelters", "sheltered", "sheltering",
                             "spurns", "spurned", "spurning", "stomps", "stomped",
                             "stomping", "suffers", "suffered", "suffering",
                             "violence", "warring")

#fairness/reciprocity
original_mfd[c(20:64),2] = c("balances", "balanced", "balancing","biased",
                             "biases", "discriminates", "discriminated",
                             "discriminating", "discrimination", "equals",
                             "equaled", "equaling", "equates", "equated",
                             "equating", "evens", "evened", "evening",
                             "excludes", "excluded", "excluding", "fairness",
                             "favors", "favored", "favoring", "honesty",
                             "impariality", "justice", "justifies", "justified",
                             "justifying", "prefers", "preferred", "preferring",
                             "prejudices", "prejudiced", "prejudicing", "reasons",
                             "reasoned", "reasoning", "rights", "tolerates",
                             "tolerated", "tolerating", "toleration")

#ingroup/loyalty
original_mfd[c(16:47),3] = c("collects", "collected", "collecting", "collective",
                             "communities", "deceives", "deceived", "deceiving",
                             "deception", "deceptions", "deserts", "deserted",
                             "deserting", "desertion", "families", "fellows",
                             "foreigners", "groups", "grouped", "grouping",
                             "indviduals", "indvidualize", "individualized",
                             "individualizing", "members", "nations", "sides",
                             "togetherness", "traits", "unites", "united", "uniting")

#authority/respect
original_mfd[c(31:112),4] = c("abides", "abided", "abiding", "authorities",
                              "classes", "classed", "classing", "command",
                              "commanded", "commanding", "controls", "controlled",
                              "controlling", "defects", "defected", "defecting",
                              "defers", "deferred", "deferring", "deference",
                              "defies", "defied", "defying", "defiance", "deserts",
                              "deserted", "deserting", "desertion", "duties",
                              "faiths", "fathers", "fathered", "fathering",
                              "honors", "honored", "honoring", "laws", "leads",
                              "leading", "mothers", "mothered", "mothering",
                              "obeys", "obeyed", "obeying", "opposes", "opposed",
                              "opposing", "orders", "ordered", "ordering", "permits",
                              "permitted", "permitting", "positions", "positioned",
                              "positioning", "preserves", "preserved", "preserving",
                              "preservation", "protests", "protested", "protesting",
                              "refuses", "refused", "refusing", "refusal", "respects",
                              "respected", "respecting", "respectful", "reveres",
                              "revered", "revering", "reverence", "serves", "served",
                              "serving", "traditions", "traditional", "traits")

#purity/sanctity
original_mfd[c(21:60),5] = c("abstains", "abstained", "abstaining", "abstinence",
                             "adulteries", "adulterous", "adulterer", "adulterers",
                             "churches", "cleans", "cleaned", "cleaning", "cleanse",
                             "cleanliness", "dirty", "diseases", "diseased", 
                             "disgusts", "disgusted", "disgusting", "grossness",
                             "innocence", "modesty", "preserves", "preserved",
                             "preserving", "preservation", "promiscuity",
                             "promiscuities", "purity", "rights", "ruins", "ruined",
                             "ruining", "sacredness", "sickness", "sicknesses",
                             "sins", "wholeness", "wholesome")

# ##separate them into h low, h high until you have ten categories 
# #harm/care
# original_mfd$h2hi[35:112] = NA 
# original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
#                       "protect", "safe", "shelter", "sympathetic",
#                       "sympathies", "benefits", "benefitted",
#                       "benefitting", "cares", "cared", "caring","defends", 
#                       "defending","defended", "guards", "guarded",
#                       "guarding","preserves",
#                       "preserved", "preserving", "protects", "protected",
#                       "protecting", "protection",  
#                       "safely", "safer", "shelters", 
#                       "sheltered", "sheltering")
# original_mfd$h2lo[61:112] = NA
# original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
#                       "damage", "danger", "destroy", "fight", "harm",
#                       "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
#                       "violent", "war","abusive",
#                       "abuser","abused","abusing","damaged",
#                       "damaging","attacked","attacking","attacker",
#                       "attacks","attackers","crushes",
#                       "crushing", "crushed", "dangerous","detroys", 
#                       "destroyed", "destroying",
#                       "fights", "fought", "fighting","harms", 
#                       "harmed", "harming", "hurts",
#                       "hurting", "kills", "killed", "killing",
#                       "ruins", "ruined", "ruining", "spurns", 
#                       "spurned", "spurning", "stomps", "stomped",
#                       "stomping", "suffers", "suffered", "suffering",
#                       "violence", "warring")
# 
# #fairness/reciprocity
# original_mfd$f2hi[41:112] = NA
# original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
#                       "fair", "honest", "just", "justify", "reason",
#                       "right", "tolerate", "impartial", "balances", 
#                       "balanced", "balancing",
#                       "equals", "equaled", "equaling", "equates", "equated",
#                       "equating", "evens", "evened", "evening","fairness",
#                       "honesty", "impartiality", "justice", "justifies", 
#                       "justified", "justifying", "reasons",
#                       "reasoned", "reasoning", "rights", "tolerates",
#                       "tolerated", "tolerating", "toleration")
# original_mfd$f2lo[25:112] = NA
# original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
#                       "prefer", "prejudice", "biased", "biases", "discriminates", 
#                       "discriminated", "discriminating", "discrimination",
#                       "excludes", "excluded", "excluding", 
#                       "favors", "favored", "favoring", "prefers", "preferred", "preferring",
#                       "prejudices", "prejudiced", "prejudicing")
# 
# #ingroup/loyalty
# original_mfd$i2hi[30:112] = NA
# original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
#                       "group", "member", "nation", "side", "together",
#                       "trait", "unite", "collects", 
#                       "collected", "collecting", "collective",
#                       "communities", "families", "fellows",
#                       "groups", "grouped", "grouping",
#                       "members", "nations", "sides",
#                       "togetherness", "traits", "unites", 
#                       "united", "uniting")
# original_mfd$i2lo[19:112] = NA 
# original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
#                       "deceives", "deceived", "deceiving",
#                       "deception", "deceptions", "deserts", "deserted",
#                       "deserting", "desertion", "foreigners",
#                       "indviduals", "indvidualize", "individualized",
#                       "individualizing")
# 
# #authority/respect
# original_mfd$a2hi[86:112] = NA
# original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
#                       "control", "defer", "duty", "faith", "father", "honor",
#                       "law", "lead", "legal", "mother", "obey", 
#                       "order", "permit", "position", "preserve",
#                       "respect", "revere", "serve", "tradtition", "trait",
#                       "abides", "abided", "abiding", "authorities",
#                       "classes", "classed", "classing", "command",
#                       "commanded", "commanding", "controls", "controlled",
#                       "controlling","defers", "deferred", "deferring", "deference",
#                       "duties","faiths", "fathers", "fathered", "fathering",
#                       "honors", "honored", "honoring", "laws", "leads",
#                       "leading", "mothers", "mothered", "mothering",
#                       "obeys", "obeyed", "obeying", "orders", 
#                       "ordered", "ordering", "permits",
#                       "permitted", "permitting", "positions", "positioned",
#                       "positioning", "preserves", "preserved", "preserving",
#                       "preservation", "respects",
#                       "respected", "respecting", "respectful", "reveres",
#                       "revered", "revering", "reverence", "serves", "served",
#                       "serving", "traditions", "traditional", "traits")
# original_mfd$a2lo[28:112] = NA
# original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
#                       "protest", "refuse", "defects", "defected", 
#                       "defecting","defies", "defied", "defying", "defiance", "deserts",
#                       "deserted", "deserting", "desertion", "opposes", "opposed",
#                       "opposing", "protests", "protested", "protesting",
#                       "refuses", "refused", "refusing", "refusal")
# 
# #purity/sanctity
# original_mfd$p2hi[32:112] = NA
# original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
#                       "preserve", "pure", "right", "sacred", "whole",
#                       "abstains", "abstained", "abstaining", "abstinence",
#                       "churches", "cleans", "cleaned", "cleaning", "cleanse",
#                       "cleanliness", "innocence", "modesty", "preserves", "preserved",
#                       "preserving", "preservation", "purity", "rights", 
#                       "sacredness", "wholeness", "wholesome")
# original_mfd$p2lo[30:112] = NA
# original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
#                       "promiscuous", "ruin", "sick", "sin", "trash",
#                       "adulteries", "adulterous", "adulterer", "adulterers",
#                       "dirty", "diseases", "diseased", "disgusts", 
#                       "disgusted", "disgusting", "grossness", "promiscuity",
#                       "promiscuities", "ruins", "ruined","ruining", 
#                       "sickness", "sicknesses", "sins")

@@

```{r process-text, eval=TRUE, include=FALSE}
##load libraries
library(tm)
library(ngram)

@@

# ##stem the original MFD stuff - separate loop on only the mfd data frame
# for(i in 1:nrow(original_mfd)) {
#   original_mfd$h2hi[i] = stemDocument(original_mfd$h2hi[i], language = "english")
#   original_mfd$h2lo[i] = stemDocument(original_mfd$h2lo[i], language = "english")
#   original_mfd$f2hi[i] = stemDocument(original_mfd$f2hi[i], language = "english")
#   original_mfd$f2lo[i] = stemDocument(original_mfd$f2lo[i], language = "english")
#   original_mfd$i2hi[i] = stemDocument(original_mfd$i2hi[i], language = "english")
#   original_mfd$i2lo[i] = stemDocument(original_mfd$i2lo[i], language = "english")
#   original_mfd$a2hi[i] = stemDocument(original_mfd$a2hi[i], language = "english")
#   original_mfd$a2lo[i] = stemDocument(original_mfd$a2lo[i], language = "english")
#   original_mfd$p2hi[i] = stemDocument(original_mfd$p2hi[i], language = "english")
#   original_mfd$p2lo[i] = stemDocument(original_mfd$p2lo[i], language = "english")
# }
# 
# final$hhisum = NA
# final$hlosum = NA
# final$fhisum = NA
# final$flosum = NA
# final$ihisum = NA
# final$ilosum = NA
# final$ahisum = NA
# final$alosum = NA
# final$phisum = NA
# final$plosum = NA
# 
# for (i in 1:nrow(final)) {
# ##first make a table of a response, unlisting everything
# temp = as.data.frame(table(unlist(strsplit(final$stemmed[i], " "))))
# ##find the rows that match the mfd list and sum and save
# final$hsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2hi[original_mfd$h2hi != "" & original_mfd$h2hi != "NA"])])
# final$hsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$h2lo[original_mfd$h2lo != "" & original_mfd$h2lo != "NA"])])
# 
# final$fsumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2hi[original_mfd$f2hi != "" & original_mfd$f2hi != "NA"])])
# final$fsumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$f2lo[original_mfd$f2lo != "" & original_mfd$f2lo != "NA"])])
# 
# final$isumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2hi[original_mfd$i2hi != "" & original_mfd$i2hi != "NA"])])
# final$isumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$i2lo[original_mfd$i2lo != "" & original_mfd$i2lo != "NA"])])
# 
# final$asumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2hi[original_mfd$a2hi != "" & original_mfd$a2hi != "NA"])])
# final$asumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$a2lo[original_mfd$a2lo != "" & original_mfd$a2lo != "NA"])])
# 
# final$psumhi[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2hi[original_mfd$p2hi != "" & original_mfd$p2hi != "NA"])])
# final$psumlo[i] = sum(temp$Freq[temp$Var1 %in% unique(original_mfd$p2lo[original_mfd$p2lo != "" & original_mfd$p2lo != "NA"])])
# }
# 
# final$hperhi = final$hsumhi / final$wordcount * 100
# final$hperlo = final$hsumlo / final$wordcount * 100
# final$fperhi = final$fsumhi / final$wordcount * 100
# final$fperlo = final$fsumlo / final$wordcount * 100
# final$iperhi = final$isumhi / final$wordcount * 100
# final$iperlo = final$isumlo / final$wordcount * 100
# final$aperhi = final$asumhi / final$wordcount * 100
# final$aperlo = final$asumlo / final$wordcount * 100
# final$pperhi = final$psumhi / final$wordcount * 100
# final$pperlo = final$psumlo / final$wordcount * 100
# 
# #let's look at the means
# tapply(final$hperhi, final$Source, mean)
# tapply(final$hperlo, final$Source, mean)
# tapply(final$fperhi, final$Source, mean)
# tapply(final$fperlo, final$Source, mean)
# tapply(final$iperhi, final$Source, mean)
# tapply(final$iperlo, final$Source, mean)
# tapply(final$aperhi, final$Source, mean)
# tapply(final$aperlo, final$Source, mean)
# tapply(final$pperhi, final$Source, mean)
# tapply(final$pperlo, final$Source, mean)
```

```{r new_data, include = FALSE}
##open the Warriner data for later
warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)

for(i in 1:nrow(warriner)) {
  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
}

####harm####

#read in the harm total words from the mtmm project
harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)

@@

#pull in the data from Warriner 
library(expss)
harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn
harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#no spurn avaliable

####Fair####
fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
#just plagiar safer
fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#nothing for just or plagiarism

#Ingroup
ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
#backstabb  benedict      best      fals   indvidu      juda    knight      true
ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])

#Authority
authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
#  abov behind   gase higher  older  taken 
authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])

#Purity
purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)

@@

```{r update-mlm, include = FALSE}
#harm_final_data clean up
#multiply by frequency and create percentage
harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100

@@

harm_model = lme(MFDweight ~ lean, 
                 data = harm_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))

#boring models first

#final model
modelfinal = lme(percent ~ valence*lean,
                 data = harm_final_data,
                 method = "ML", 
                 na.action = "na.omit", 
                 random = list(~1|Var1, ~1|Source))
summary(modelfinal)

with(harm_final_data, tapply(percent, list(lean), mean))
with(harm_final_data, tapply(valence, list(lean), mean, na.rm = T))
with(harm_final_data, tapply(weighted, list(lean), mean, na.rm = T))

modelfinal = lme(weighted ~ lean,
                 data = harm_final_data,
                 method = "ML", 
                 na.action = "na.omit", 
                 random = list(~1|Var1, ~1|Source))
summary(modelfinal)

```{r mlm-analyses, echo=FALSE, warning=FALSE, include = FALSE}
##Attempt at MLM
mlm_data = final[ , -c(3:28) ]
long_mlm = melt(mlm_data,
                id = c("X", "Source"))
colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
long_mlm$lean = factor(long_mlm$Source,
                       levels = names(table(long_mlm$Source)),
                       labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
long_mlm$lean = gsub("1", "", long_mlm$lean)

#####intercept only model####
##gls = generalized least squares
##ML = maximum likelihood
model1 = gls(percent ~ 1, 
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit")
summary(model1)

####overall percent - random intercept by source####
model3 = lme(percent ~ 1,
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model3)
r.squaredGLMM(model3)

####separate models by type####
##MFD category ~ lean 
model4.1 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.1)
r.squaredGLMM(model4.1)

model4.2 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.2)
r.squaredGLMM(model4.2)

model4.3 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.3)
r.squaredGLMM(model4.3)

model4.4 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.4)
r.squaredGLMM(model4.4)

model4.5 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.5)
r.squaredGLMM(model4.5)

model4.6 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.6)
r.squaredGLMM(model4.6)

model4.7 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.7)
r.squaredGLMM(model4.7)

model4.8 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.8)
r.squaredGLMM(model4.8)

model4.9 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.9)
r.squaredGLMM(model4.9)

model4.10 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.10)
r.squaredGLMM(model4.10)

```{r model-table, results='asis', echo=FALSE}
tableprint = matrix(NA, nrow = 12, ncol = 7)

colnames(tableprint) = c("Model", "AIC", "BIC", "$\\chi^2$", "$df$",
                         "$R^2_m", "$R^2_c")

#put in each model set information
#temp store model summary
temp = summary(model1)

#put in the information
#entered a raw number here, as a reminder
tableprint[1 , ] = c("Non-Random Intercept", temp$AIC, temp$BIC,
                     temp$logLik, 30409, "-", "-")

temp = summary(model3)
tableprint[2 , ] = c("Random Intercept", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms, r.squaredGLMM(model3))

temp = summary(model4.1)
tableprint[3 , ] = c("Harm High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.1))

temp = summary(model4.2)
tableprint[4 , ] = c("Harm Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.2))

temp = summary(model4.3)
tableprint[5 , ] = c("Fairness High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.3))

temp = summary(model4.4)
tableprint[6 , ] = c("Fairness Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.4))

temp = summary(model4.5)
tableprint[7 , ] = c("Ingroup High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.5))

temp = summary(model4.6)
tableprint[8 , ] = c("Ingroup Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.6))

temp = summary(model4.7)
tableprint[9 , ] = c("Authority High", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.7))

temp = summary(model4.8)
tableprint[10 , ] = c("Authority Low", temp$AIC, temp$BIC,
                     temp$logLik, temp$fixDF$terms[1], r.squaredGLMM(model4.8))

>>>>

---
title             : "Moral Foundations of U.S. Political News Organizations"
shorttitle        : "MORAL NEWS"

@@

```{r load_packages, include = FALSE}
library(papaja) 
library(MuMIn)
library(reshape)
library(nlme)
library(ggplot2)
library(expss)

@@

```{r data-cleanup, eval=FALSE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

write.csv(final, "finaldata.csv")

@@

@@

```{r stem_text, eval=TRUE, include=FALSE}

final = read.csv("finaldata.csv", stringsAsFactors = F)
final = na.omit(final) #one weird NA line

##load libraries
library(tm)
library(ngram)

@@

```{r stem_warriner, include = FALSE}
##open the Warriner data for later
warriner = read.csv("BRM-emot-submit.csv", stringsAsFactors = F) #want v.mean.sum
warriner$V.Mean.Sum = scale(warriner$V.Mean.Sum)

for(i in 1:nrow(warriner)) {
  warriner$Word2[i] = stemDocument(warriner$Word[i], language = "english")
} 
```

```{r create_datasets_harm, include=FALSE}
#read in the harm total words from the mtmm project
harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)

@@

#pull in the data from Warriner 
harm_final_data$valence = vlookup(harm_final_data$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#figure out stupid words
table(harm_final_data$Var1[is.na(harm_final_data$valence) & harm_final_data$Freq > 0])
#fought, safer, spurn
harm_final_data$valence[harm_final_data$Var1 == "fought"] = warriner$V.Mean.Sum[warriner$Word2 == "fight"]
harm_final_data$valence[harm_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#no spurn avaliable
```

```{r create_datasets_fair, include=FALSE}
fair_all = read.csv("fair_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(fair_final_data$Var1[is.na(fair_final_data$valence) & fair_final_data$Freq > 0])
#just plagiar safer
fair_final_data$valence[fair_final_data$Var1 == "safer"] = warriner$V.Mean.Sum[warriner$Word2 == "safe"]
#nothing for just or plagiarism
```

```{r create_datasets_ingroup, include=FALSE}
ingroup_all = read.csv("ingroup_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(ingroup_final_data$Var1[is.na(ingroup_final_data$valence) & ingroup_final_data$Freq > 0])
#backstabb  benedict      best      fals   indvidu      juda    knight      true
ingroup_final_data$valence[ingroup_final_data$Var1 == "fals"] = warriner$V.Mean.Sum[warriner$Word2 == "FALSE"]
ingroup_final_data$valence[ingroup_final_data$Var1 == "indvidu"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "individu"])
ingroup_final_data$valence[ingroup_final_data$Var1 == "true"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "TRUE"])
```

```{r create_datasets_authority, include=FALSE}
authority_all = read.csv("authority_words_total.csv", stringsAsFactors = F)

@@

#figure out stupid words
table(authority_final_data$Var1[is.na(authority_final_data$valence) & authority_final_data$Freq > 0])
#  abov behind   gase higher  older  taken 
authority_final_data$valence[authority_final_data$Var1 == "gase"] = warriner$V.Mean.Sum[warriner$Word2 == "gas"]
authority_final_data$valence[authority_final_data$Var1 == "higher"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "high"])
authority_final_data$valence[authority_final_data$Var1 == "older"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "old"])
authority_final_data$valence[authority_final_data$Var1 == "taken"] = mean(warriner$V.Mean.Sum[warriner$Word2 == "take"])
```

```{r create_datasets_purity, include=FALSE}
purity_all = read.csv("purity_words_total.csv", stringsAsFactors = F)

@@

```{r analysis_harm, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
harm_final_data$weight = harm_final_data$Freq * harm_final_data$valence / harm_final_data$wordcount * 100

@@

harm_model = lme(MFDweight ~ lean, 
                 data = harm_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(harm_model)
```

```{r analysis_fair, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
fair_final_data$weight = fair_final_data$Freq * fair_final_data$valence / fair_final_data$wordcount * 100

#flatten down to sum by article 
fair_final_temp = aggregate(fair_final_data$weight, 
          by = list(fair_final_data$URL),
          FUN = sum, na.rm = T)
colnames(fair_final_temp) = c("URL", "MFDweight")

fair_final_temp$lean[grepl("nytimes.com", fair_final_temp$URL) |
                       grepl("npr.org", fair_final_temp$URL)] = "Liberal"
fair_final_temp$lean[grepl("breitbart.com", fair_final_temp$URL) |
                       grepl("foxnews.com", fair_final_temp$URL)] = "Conservative"

fair_final_temp$Source[grepl("nytimes.com", fair_final_temp$URL)] = "NY Times"
fair_final_temp$Source[grepl("npr.org", fair_final_temp$URL)] = "NPR"
fair_final_temp$Source[grepl("foxnews.com", fair_final_temp$URL)] = "Fox"
fair_final_temp$Source[grepl("breitbart.com", fair_final_temp$URL)] = "Breitbart"

fair_model = lme(MFDweight ~ lean, 
                 data = fair_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(fair_model)
```

```{r analysis_ingroup, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
ingroup_final_data$weight = ingroup_final_data$Freq * ingroup_final_data$valence / ingroup_final_data$wordcount * 100

#flatten down to sum by article 
ingroup_final_temp = aggregate(ingroup_final_data$weight, 
          by = list(ingroup_final_data$URL),
          FUN = sum, na.rm = T)
colnames(ingroup_final_temp) = c("URL", "MFDweight")

ingroup_final_temp$lean[grepl("nytimes.com", ingroup_final_temp$URL) |
                       grepl("npr.org", ingroup_final_temp$URL)] = "Liberal"
ingroup_final_temp$lean[grepl("breitbart.com", ingroup_final_temp$URL) |
                       grepl("foxnews.com", ingroup_final_temp$URL)] = "Conservative"

ingroup_final_temp$Source[grepl("nytimes.com", ingroup_final_temp$URL)] = "NY Times"
ingroup_final_temp$Source[grepl("npr.org", ingroup_final_temp$URL)] = "NPR"
ingroup_final_temp$Source[grepl("foxnews.com", ingroup_final_temp$URL)] = "Fox"
ingroup_final_temp$Source[grepl("breitbart.com", ingroup_final_temp$URL)] = "Breitbart"

ingroup_model = lme(MFDweight ~ lean, 
                 data = ingroup_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(ingroup_model)
```

```{r analysis_authority, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
authority_final_data$weight = authority_final_data$Freq * authority_final_data$valence / authority_final_data$wordcount * 100

#flatten down to sum by article 
authority_final_temp = aggregate(authority_final_data$weight, 
          by = list(authority_final_data$URL),
          FUN = sum, na.rm = T)
colnames(authority_final_temp) = c("URL", "MFDweight")

authority_final_temp$lean[grepl("nytimes.com", authority_final_temp$URL) |
                       grepl("npr.org", authority_final_temp$URL)] = "Liberal"
authority_final_temp$lean[grepl("breitbart.com", authority_final_temp$URL) |
                       grepl("foxnews.com", authority_final_temp$URL)] = "Conservative"

authority_final_temp$Source[grepl("nytimes.com", authority_final_temp$URL)] = "NY Times"
authority_final_temp$Source[grepl("npr.org", authority_final_temp$URL)] = "NPR"
authority_final_temp$Source[grepl("foxnews.com", authority_final_temp$URL)] = "Fox"
authority_final_temp$Source[grepl("breitbart.com", authority_final_temp$URL)] = "Breitbart"

authority_model = lme(MFDweight ~ lean, 
                 data = authority_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(authority_model)
```

```{r analysis_purity, include = FALSE}
#final_data clean up
#multiply by frequency and create percentage
purity_final_data$weight = purity_final_data$Freq * purity_final_data$valence / purity_final_data$wordcount * 100

#flatten down to sum by article 
purity_final_temp = aggregate(purity_final_data$weight, 
          by = list(purity_final_data$URL),
          FUN = sum, na.rm = T)
colnames(purity_final_temp) = c("URL", "MFDweight")

purity_final_temp$lean[grepl("nytimes.com", purity_final_temp$URL) |
                       grepl("npr.org", purity_final_temp$URL)] = "Liberal"
purity_final_temp$lean[grepl("breitbart.com", purity_final_temp$URL) |
                       grepl("foxnews.com", purity_final_temp$URL)] = "Conservative"

purity_final_temp$Source[grepl("nytimes.com", purity_final_temp$URL)] = "NY Times"
purity_final_temp$Source[grepl("npr.org", purity_final_temp$URL)] = "NPR"
purity_final_temp$Source[grepl("foxnews.com", purity_final_temp$URL)] = "Fox"
purity_final_temp$Source[grepl("breitbart.com", purity_final_temp$URL)] = "Breitbart"

purity_model = lme(MFDweight ~ lean, 
                 data = purity_final_temp, 
                 method = "ML",
                 na.action = "na.omit",
                 random = list(~1|Source))
summary(purity_model)
```
